Extended Data

### 2021-10-13 doc/manuscript/Dow_Extended_Data.Rmd
knit in new Extended Data Fig. 2
@camerondow35 , FYI, this and other figure captions still need some details filled in/ word-smithing

growth_curves_all_caption  <- " **Extended Data Figure 2 | Growth trajectories for ring- and diffuse-porous trees, as both relative and cumulative fractions of total annual growth.** Each line represents one year's growth for a given tree, fit with McMahon model. " #needs wordsmithing!!!

>>>>

growth_curves_all_caption  <- " **Extended Data Figure 2 | Phenological patterns of forest canopy greenness (top row) and stem growth of ring- and diffuse-porous trees, represented as both relative and cumulative fractions of total annual growth (middle and bottom rows, respectively), at our two focal study sites** In the top row, canopy greenness is characterized using the two band Enhanced Vegetation Index (EVI2) ..., with each line representing a year between 2001 and 2018. For stem growth, each line represents one year's growth for a given tree, fit with McMahon model. " #needs wordsmithing!!!
